Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
clarify chat/im

\begin{itemize}
\item \libpurple makes a distinction between "IMs" (two-person chats) and
"chats" (three or more people); \libmotmot does not.  \libpurple takes in
different arguments for its IM-related and its chat-related functions

>>>>

\begin{itemize}
\item \libpurple makes a distinction between ``IMs'' and
``chats''; \libmotmot does not.  (In particular, IMs are defined as a direct two-person communication only, whereas chats are an overarching category that can involve one, two, or more users.) \libpurple takes in
different arguments for its IM-related and its chat-related functions
